Supplemental Materials

### 2021-06-21 supplement/supplement-main.Rmd
supp updates

@@

plt.valid <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=corrDF, aes(label=paste("r =", round(cor,2))),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1)) +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

# create plot of differences for all 14 scales

s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank()
    ) +
  labs(title="Study 2", y = "Mean difference", x = "Belief scale", color="Intervention")
```

@@

make_table <- function(fit, caption=NULL){
  fit_sum <- summary(fit)

@@

  kableExtra::kbl(tbl_sum, digits = 2, booktabs = T, caption=caption) %>% 
    kableExtra::kable_classic(full_width=F)
}

make_table(fit_s2_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")

@@

```{r s2_model_pred, echo=FALSE, fig.height=4, fig.width=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 2. Error bars represent 95\\% confidence intervals."}
# Generate model predictions + create plot
# odd, I remember the results being slightly better than this, job talk says r=.87
obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")

(obs_pred_plot <- obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2.5) +
  geom_errorbar(alpha=.5, width=0) +
  annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
  coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
  theme_bw(base_size=14) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1)) +
  labs(title="Belief changes", subtitle="Experiment 2")

@@

```{r echo=F, fig.width=8, fig.height=4}
## combined plot for paper
library(patchwork)

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")

@@

s2_diff_plot + s2_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
```

@@

```{r echo=F, message=F}

@@

interv_sim %>%
  ggplot(aes(x=abs(correlation), y = model_pred)) +
  geom_point()

(pred_change_plot <- interv_sim %>% 
  filter(scale!="vaccIntent") %>%
    mutate(scale = recode_nodes2(scale)) %>% 
  ggplot(aes(x=reorder(scale, model_pred), y = model_pred)) + 
  geom_bar(stat="identity") + 
  coord_flip() +
  labs(x="Targeted belief", y = "Predicted change in intentions") +
  theme_bw(base_size=22) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1.5))

@@

s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank()
    ) +
  labs(title="Study 3a and 3b", y = "Mean difference", x = "Belief scale", color="Intervention")

@@

```{r, echo=FALSE, message=F, warning=F}
# compare conditions on vaccIntent w/ regression model
# -- TODO: recode phase/condition 5/25/21, 11:07 AM
s3_reg <- s3_long %>% 
  filter(scale=="vaccIntent") %>% 
  mutate(
    phase = relevel(factor(phase), ref="pre"),
    condition = relevel(factor(condition), ref="noInterv"),
    response = resp
    )

@@

make_table(fit_s3_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3.")
```

@@

```{r, echo=F, fig.width=4, fig.height=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 3. Error bars represent 95\\% confidence intervals."}

@@

# fit evidence node
obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")

(
  obs_pred_plot <- obs_pred %>% 
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2.5) +
  geom_errorbar(alpha=.5, width=0) +
  # coord_fixed(ratio=1) +
  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
  annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
  theme_bw(base_size=14) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1) +
  labs(title="Belief changes",subtitle="Experiment 3a & 3b")
)
```

```{r fig.width=8, fig.height=4}
s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.6,.15),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention")

@@

s3_diff_plot + s3_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
```

@@

s4_meta <- list(
  n_recruited = s4_wide %>% filter(workerId %in% s1_all$workerId) %>%  distinct(workerId) %>% nrow(),
  n_recruited_post = s4_wide %>% filter(workerId %in% s1_all$workerId) %>%  distinct(workerId) %>% nrow(),
  n_failed_post = s4_wide %>% 
    filter(check_5!=5 | check_3!=3) %>% 
    filter(workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow(), #%>% ,
  n_complete =s4_wide %>% 
    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow()
)
```

@@

combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
  geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  # facet_wrap(~scale, scales="free") +
  theme_bw(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "right",
    panel.grid = element_blank()) +
  labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")
```

@@

make_table(fit_s4_vaccIntent, "Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
```

@@

(obs_pred_plot <- obs_pred %>% # a bit of a hack
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_point(size=2.5) +
  geom_errorbar(alpha=.5, width=0) +
  annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
  coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
  theme_bw(base_size=14) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1)) +
  labs(title="Belief changes",subtitle="Study 4 - vaccIntent")

@@

```{r fig.width=8, fig.height=4}
s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2, shape=16) +
  geom_errorbar(position=position_dodge(width=.25), width=0, alpha=.8) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.85),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure")

@@

s4_diff_plot + s4_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))
```

@@

The table below presents demographic information for participants across all four studies.

@@

>>>>

```{r}
## explore cpdag

main_cpdag <- cpdag(main_model)

# do plotting -- will likely see lots of ambiguity??
plot(main_cpdag)

# CPDAG edge directions ruled out by blacklist (10)
ruled_out <- inner_join(as.data.frame(undirected.arcs(main_cpdag)), as.data.frame(theory_bl), by=c("from","to"))

# leaves 5 arcs that are unconstrained by both data and theory
anti_join(as.data.frame(undirected.arcs(main_cpdag)), (ruled_out %>% bind_rows(ruled_out %>% rename(to="from", from="to")) ), by = c("from", "to"))

# most substantive are vaccTox <--> vaccDanger, vaccEff
```

@@

plt.valid <- test_analyze %>%
  mutate(varName = recode_nodes(varName)) %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="#0067B1") + 
  geom_text(data=corrDF, aes(label=paste("r =", round(cor,2))),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1)) +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

# create plot of differences for all 14 scales
# 
# s2_scored %>% 
#   spread(phase, mean) %>% 
#   drop_na(scale) %>% 
#   mutate(diff = post-pre) %>% 
#   mutate(
#     scale = recode_nodes2(scale),
#     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
#     ) %>% 
#   group_by(condition, scale) %>%
#   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
#   ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
#   geom_pointrange(position=position_dodge(width=.25)) +
#   geom_hline(yintercept=0, linetype="dashed", color="grey") +
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(angle=45, hjust=1),
#     panel.grid = element_blank()
#     ) +
#   labs(title="Study 2", y = "Mean difference", x = "Belief scale", color="Intervention")
```

@@

make_table_df <- function(fit){
  fit_sum <- summary(fit)

@@

  return(tbl_sum)
}

make_table <- function(table_df, caption=NULL){

  kableExtra::kbl(table_df, digits = 2, booktabs = T, caption=caption) %>% 
    kableExtra::kable_classic(full_width=F)
}

fit_s2_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(diseaseRisk|post)","", Term)
    )
  ) %>% 
  make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 2.")

@@

```{r s2_model_pred, echo=FALSE, fig.height=4, fig.width=4, fig.align="center", fig.cap="Mean observed and predicted change scores for Experiment 2. Error bars represent 95\\% confidence intervals."}
# Generate model predictions + create plot
# odd, I remember the results being slightly better than this, job talk says r=.87
# obs_pred <- make_pred_df(s2_mdf, base_model, "diseaseSevere")
# 
# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
# 
# (obs_pred_plot <- obs_pred %>% # a bit of a hack
#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
#   geom_point(size=2.5) +
#   geom_errorbar(alpha=.5, width=0) +
#   annotate(geom="text", x=.03, y=-.04, label= paste("r =", cor_val)) +
#   coord_cartesian(xlim=c(-.06,.06), ylim=c(-.06,.06)) +
#   theme_bw(base_size=14) +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
#   theme(aspect.ratio = 1)) +
#   labs(title="Belief changes", subtitle="Experiment 2")

@@

```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiment 2. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions. Right, mean observed and model predicted change scores for the disease risk intervention condition. In both plots, error bars represent 95\\% confidence intervals."}
## combined plot for paper
library(patchwork)

s2_diff_plot <- s2_scored %>% 
  spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.9),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")

@@

s2_plt <- s2_diff_plot + s2_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))

s2_plt
```

@@

```{r echo=F, message=F, fig.align='center', fig.height=3, fig.width=3}

@@

# interv_sim %>%
#   ggplot(aes(x=abs(correlation), y = model_pred)) +
#   geom_point()

(pred_change_plot <- interv_sim %>% 
  filter(scale!="vaccIntent") %>%
    mutate(scale = recode_nodes2(scale)) %>% 
  ggplot(aes(x=reorder(scale, model_pred), y = model_pred)) + 
  geom_bar(stat="identity", fill = "#0067B1") + 
  coord_flip() +
  labs(x="Targeted belief", y = "Predicted change\nin intentions") +
  theme_bw(base_size=10) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(aspect.ratio = 1))

@@

# s3_scored %>% 
#   # spread(phase, mean) %>% 
#   drop_na(scale) %>% 
#   mutate(diff = post-pre) %>% 
#   mutate(
#     scale = recode_nodes2(scale),
#     condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
#     ) %>% 
#   group_by(condition, scale) %>%
#   summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
#   ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition)) +
#   geom_pointrange(position=position_dodge(width=.25)) +
#   geom_hline(yintercept=0, linetype="dashed", color="grey") +
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(angle=45, hjust=1),
#     panel.grid = element_blank()
#     ) +
#   labs(title="Study 3a and 3b", y = "Mean difference", x = "Belief scale", color="Intervention")

@@

```{r, echo=FALSE, message=F, warning=F}
# compare conditions on vaccIntent w/ regression model

# -- TODO: recode phase/condition 5/25/21, 11:07 AM
s3_reg <- s3_long %>% 
  filter(scale=="vaccIntent") %>% 
  mutate(
    phase = relevel(factor(phase), ref="pre"),
    condition = relevel(factor(condition), ref="noInterv"),
    response = resp
    )

@@

fit_s3_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3.")
```

We also analyzed each experiment individually.

```{r, echo=FALSE, message=F, warning=F}

fit_s3a_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s3_reg %>% filter(study=="A"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.95),
  seed = 69568,
  file = "../local/fit_s3a_vaccIntent.rds"
)

fit_s3b_vaccIntent <- brm(
  response ~ phase*condition + (1|item) + (1|workerId),
  family = cumulative("logit"),
  data = s3_reg %>% filter(study=="B"),
  chains = 6,
  cores = 6,
  control = list(adapt_delta=.95),
  seed = 69568,
  file = "../local/fit_s3b_vaccIntent.rds"
)

fit_s3a_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3a.")

fit_s3b_vaccIntent %>% 
  make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|post)","", Term)
    )
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Experiment 3b.")
```

@@

```{r, echo=F, fig.width=4, fig.height=4, fig.align="center", fig.cap="Plots of belief changes following the intervention in Experiment 3. Left, mean difference scores from pretest to posttest for the 14 belief scales measured in Experiment 3. Mean observed and predicted change scores for Experiment 3. Error bars in both plots represent 95\\% confidence intervals. "}

@@

# fit evidence node
# obs_pred <- make_pred_df(s3_mdf, base_model, "vaccTox")
# 
# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
# 
# (
#   obs_pred_plot <- obs_pred %>% 
#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
#   geom_point(size=2.5) +
#   geom_errorbar(alpha=.5, width=0) +
#   # coord_fixed(ratio=1) +
#   coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
#   annotate(geom="text", x=.05, y=-.1, label= paste("r =", cor_val)) +
#   theme_bw(base_size=14) +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
#   theme(aspect.ratio = 1) +
#   labs(title="Belief changes",subtitle="Experiment 3a & 3b")
# )
```

```{r fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions. Right, mean observed and model predicted change scores for the toxins intervention condition. In both plots, error bars represent 95\\% confidence intervals."}
s3_diff_plot <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = ifelse(condition=="noInterv", "Control", "Disease Risk")
    ) %>% 
  group_by(condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ggplot(aes(x = reorder(scale,M), y = M, ymin = M-se*2, ymax=M+se*2, color=condition, shape=condition)) +
  geom_pointrange(position=position_dodge(width=.25)) +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=c("#0067b1","#c50024")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.6,.15),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="Intervention", shape="Intervention")

@@

s3_plt <- s3_diff_plot + s3_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))

s3_plt
```

@@

s4_meta <- list(
  n_recruited = s4_wide %>% filter(workerId %in% s1_all$workerId) %>%  distinct(workerId) %>% nrow(),
  n_recruited_post = s4_wide %>% filter(workerId %in% s1_all$workerId) %>%  distinct(workerId) %>% nrow(),
  n_failed_post = s4_wide %>% 
    filter(check_5!=5 | check_3!=3) %>% 
    filter(workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow(), #%>% ,
  n_complete =s4_wide %>% 
    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% distinct(workerId) %>% nrow(),
  n_news = s4_wide %>%
    filter(check_5==5, check_3==3, workerId %in% s1_all$workerId) %>% 
    filter(vacc_news==1) %>% 
    distinct(workerId) %>% 
    nrow()
)
```

@@

# combined %>% 
#   filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
#   mutate(diff = posttest-pretest) %>%
#   mutate(
#     vacc_news = as.factor(vacc_news),
#     scale = recode_nodes2(scale)
#     ) %>%
#   group_by(vacc_news,scale) %>%
#   summarize(
#     mean = mean(diff),
#     se = sd(diff)/sqrt(n()),
#     ul = mean + se,
#     ll = mean - se,
#     ul95 = mean + 1.96*se,
#     ll95 = mean - 1.96*se
#   ) %>%
#   ungroup() %>%
#   mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
#   # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
#   ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll, ymax=ul, color=vacc_news)) +
#   geom_point(position=position_dodge(width=.25), size=2, shape=16) +
#   geom_errorbar(position=position_dodge(width=.25), size=.75, width=0, alpha=.8) +
#   geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
#   geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
#   # facet_wrap(~scale, scales="free") +
#   theme_bw(base_size = 12) +
#   theme(
#     axis.text.x = element_text(angle = 45, hjust = 1), 
#     legend.position = "right",
#     panel.grid = element_blank()) +
#   labs(title="Study 4", y = "Change scores", x = "Belief scale", color ="News\nexposure")
```

@@

fit_s4_vaccIntent %>% 
make_table_df() %>% 
  mutate(
    Term = case_when(
      # grepl("(diseaseRisk|post)", Term) ~ paste0("$\\beta{", 
      #                                            gsub("(diseaseRisk|post)", "", Term),
      #                                            "}$"),
      grepl("Intercept\\[", Term) ~ gsub("Intercept\\[(.*)\\]","$\\\\alpha_{\\1}$", Term),
      Term == "item_sd(Intercept)" ~ "$\\sigma_{item}$",
      Term == "subj_sd(Intercept)" ~ "$\\sigma_{subj}$",
      TRUE ~ gsub("(intervention|posttest)","", Term)
    ),
    Term = gsub("vacc_news", "awareness", Term)
  ) %>% 
make_table("Bayesian regression model coefficients for model of Vaccine Intentions in Study 4.")
```

@@

# obs_pred <- make_pred_df(s4_mdf, base_model, "vaccIntent")
# 
# cor_val <- round(cor(obs_pred$predicted, obs_pred$observed),3)
# 
# (obs_pred_plot <- obs_pred %>% # a bit of a hack
#   ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul)) +
#   geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
#   geom_point(size=2.5) +
#   geom_errorbar(alpha=.5, width=0) +
#   annotate(geom="text", x=.04, y=-.04, label= paste("r =", cor_val)) +
#   coord_cartesian(xlim=c(-.07,.06), ylim=c(-.07,.06)) +
#   theme_bw(base_size=14) +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
#   theme(aspect.ratio = 1)) +
#   labs(title="Belief changes",subtitle="Study 4 - vaccIntent")

@@

```{r echo=F, warning=F, message=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Study 4. Left, mean difference scores from pretest to posttest for the 14 belief scales among participants who did and did not report exposure to news of the 2019 Measles outbreak in New York. Right, mean observed and model predicted change scores for those who were exposed to news of the outbreak. In both plots, error bars represent 95\\% confidence intervals."}
s4_diff_plot <- combined %>% 
  filter(returned==TRUE, !is.na(vacc_news)) %>% # somehow 5? participants slippd by without answering 
  mutate(diff = posttest-pretest) %>%
  mutate(
    vacc_news = as.factor(vacc_news),
    scale = recode_nodes2(scale)
    ) %>%
  group_by(vacc_news,scale) %>%
  summarize(
    mean = mean(diff),
    se = sd(diff)/sqrt(n()),
    ul = mean + se,
    ll = mean - se,
    ul95 = mean + 1.96*se,
    ll95 = mean - 1.96*se
  ) %>%
  ungroup() %>%
  mutate(vacc_news = factor(vacc_news, c(1,0), labels=c("Yes","No"))) %>%
  # mutate(phase = ordered(phase, levels=c("pretest","posttest"))) %>%
  ggplot(aes(x=reorder(scale, mean), y = mean, ymin =ll95, ymax=ul95, color=vacc_news, shape=vacc_news)) +
  geom_point(position=position_dodge(width=.25), size=2) +
  geom_errorbar(position=position_dodge(width=.25), width=0) +
  # geom_errorbar(aes(ymin=ll95, ymax = ul95), width=0, position=position_dodge(width=.25), alpha=.5) +
  geom_hline(yintercept = 0, linetype="dashed",alpha=.5) +
  scale_color_manual(values=c("#0067b1","grey")) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.35,.85),
    legend.direction = "horizontal",
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", color="News Exposure", shape="News Exposure")

@@

s4_plt <- s4_diff_plot + s4_obs_pred_plot + plot_layout(ncol=2, widths = c(2,1))

s4_plt
```

@@

The table below presents demographic information for participants across all five studies.

@@

```{r exports_for_paper, include=F}
